Age-related changes in plant growth and traits

### 2015-08-06 results_growth_short.Rmd
new file on details of errors to fix - same info as in "issues" I've posted
new file that is follow up on today's conversation with Mark and needs to be intregrated into other files

continued bits of other work, mostly trying to tidy up accessory tissue thoughts

mod <- lm(log(prop_growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,growth_height>0&species!="PEPU"&species!="PELA"&species!="COER"))
plot((RA+.01)~(prop_growth_height), data=subset(SummaryInd,species!="PEPU"&species!="PELA"), log="xy", col=col.spp[as.factor(species)],pch=16)
```

```{r, echo=FALSE,message=FALSE, warning=FALSE}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_stem_diam"
xvar <- "RA"

@@

mtext("RA", 1, outer=TRUE,cex=1.2)
mtext("Yearly increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
```
###PCA analysis indicates the same two patterns
* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
* Orthoganal to these in WD vs. maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
* I interpret this to mean that the three traits (Hmax, LMA, WD) strongly influence each other - presumably, Hmax a function of WD and LMA), but do not particularly 
* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals, greatly reducing sample size. Including these variables, doesn't change the basic story.
* fine tuning:  
  ** remove RGR leaf (similar to RGR)
  ** remove prop_max_weight and prop_max_repro (similar to prop_maxH)

>>>>

mod <- lm(log(prop_growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,growth_height>0&species!="PEPU"&species!="PELA"&species!="COER"))
plot((RA+.01)~(prop_growth_height), data=subset(SummaryInd,species!="PEPU"&species!="PELA"), log="xy", col=col.spp[as.factor(species)],pch=16)
```
```{r, echo=FALSE,message=FALSE, warning=FALSE}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_stem_diam"
xvar <- "RA"

@@

mtext("RA", 1, outer=TRUE,cex=1.2)
mtext("Yearly increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
```

```{r, echo=FALSE,message=FALSE, warning=FALSE}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "RA"
xvar <- "age"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",
                    main=spp,xlim=c(1,35))
}

mtext("RA", 1, outer=TRUE,cex=1.2)
mtext("age", 2, outer=TRUE,cex=1.2)
```

```{r, echo=FALSE,message=FALSE, warning=FALSE}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "RA"
xvar <- "diameter"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",
                    main=spp)
}

mtext("RA", 1, outer=TRUE,cex=1.2)
mtext("basal diameter", 2, outer=TRUE,cex=1.2)
```

###PCA analysis indicates the same two patterns
* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
* Orthoganal to these in WD vs. maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
* I interpret this to mean that the three traits (Hmax, LMA, WD) strongly influence each other - presumably, Hmax a function of WD and LMA), but do not particularly 
* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals, greatly reducing sample size. Including these variables, doesn't change the basic story.
* fine tuning:  
  ** remove RGR leaf (similar to RGR)
  ** remove prop_max_weight and prop_max_repro (similar to prop_maxH)
